\SW: II. New lens candidates from the CFHTLS discovered through citizen science

### 2015-03-25 doc/sw-cfhtls.tex
Merged bib files into one giant file. Closes #109
Re-worded appendix to use Power instead of Skill, #110

Here, we investigate if the skill\footnote{see the
\Aref{appendix:skill} for the choice of this term and how it is
different from that used in paper I} of volunteers is systematically
different between the sample of detected and missed lenses.

@@

\section{Skill}
\label{appendix:skill}
In paper I, the term skill is given by the expectation value of the
information gain which is related to the P$_{\rm L}$, the probability to
correctly identify a lens as a lens and P$_{\rm D}$, the probability to
correctly identify a dud as a dud. The skill is not linearly related to
 P$_{\rm L}$ and P$_{\rm D}$. One can get the same value of
skill for different combinations of P$_{\rm L}$ and P$_{\rm D}$ (see
Fig. XXX).

\question{AM}{PJM, Is it useful to have this description, any other comments on
this section?}
{\bf AM: add figure and polish this further upon suggestion from PJM}

As described in the appendix of paper I, the posterior probability P is
related to the volunteers skill (or information gain). Also, a volunteer
with a given skill, will have different positive ($\Delta$~log(P)) and
negative (-$\Delta$~log(P)) kicks on the trajectory plot. Thus, it is
not useful to compare classifications of high and low skill volunteers
to understand if there is a difference in their performance and if the
high skill volunteers can increase the completeness of the lenses. For
example, a volunteer who is very good at rejecting duds and not so good
at identifying lenses will still have a high skill. But such a
volunteer will fail to detect many of the interesting lenses. Therefore,
we do not compare high skill vs. low skill volunteers to address this
issue.

For lack of a better word, we also use the same term skill which has a
similar meaning to that described in Paper I but not identical. We use a
more qualitative definition implying the ability of the volunteers to
make correct lens identification.

@@

\bibliographystyle{apj}
\bibliography{references_cfhtls}
%\bibliography{references}

>>>>

Here, we investigate if the skill\footnote{see the
\Aref{appendix:power} for the choice of this term and how it is
different from that used in paper I} of volunteers is systematically
different between the sample of detected and missed lenses.

@@

\section{Lens Detection Power}
\label{appendix:power}

In \PaperOne, we defined the ``Skill'' of an agent as being given by the
expectation value of the information gain per classification. This quantity is a
non-linear function of both the $P_{\rm L}$, the probability of correctly
identifying a lens as a lens and $P_{\rm D}$, the probability of correctly
identifying a dud as a dud. This means that one can get the same value of Skill
for different combinations of $P_{\rm L}$ and $P_{\rm D}$ (see Fig. XXX) -- it
reflect the all-round ability of a classifier to contribute information.

As described in the appendix of \PaperOne, the posterior probability $P$ of a
subject is determined by the $P_{\rm L}$ and $P_{\rm D}$ of all the volunteers
who marked it, via Bayes' Theorem. Each agent will apply a different ``kick'' to
the subject probability, $\Delta\log(P)$, which can be either positive (if the
classifier thinks it contains a lens) or negative (if they don't). These kicks
appear as steps on the subject's trajectory plot. This kick magnitude gives a useful measure of an agent's ``Power'' to move subjects closer to detection.
Note that a volunteer who is very good at rejecting duds, but not so good
at identifying lenses, may have a high Skill but a low Power (since they may fail to detect many of the interesting lenses): Power provides a more precise quantification of a classifier's ability to detect lenses.

@@

\bibliographystyle{apj}
\bibliography{references}
%\bibliography{references}
